Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2022-11-21 ms/ms03_results.tex
MS

\subsection*{How specific are pleiotropic eQTLs to traits, genes and tissues?}

Next I explored the trait, gene and cell type/tissue specificity of colocalized eQTL/GWAS variants.
%
74\% of eQTLs are involved in one GWAS class, 21\% are involved in 2 classes and the remaining variants with 3 or more trait classes make less that 4\% of eQTLs (Fig. \ref{fig:hist_gwas_egene_etissue}(a).
%
Regarding target genes, 36\% of the colocalized eQTLs modulate a single gene, 24\% modulate two genes, and the remaining 40\% modulate three or more genes (Fig. \ref{fig:hist_gwas_egene_etissue}(b).
%
Concerning cell types and tissues classes, 27\% are active in a single tissue, 16\% in two tissues, 11\% in three tissues, and the remaining 46\% in four or more tissues (Fig. \ref{fig:hist_gwas_egene_etissue}(c).
%
In conclusion, most colocalized eQTL/GWAS variants are specific to one GWAS trait.
%
By contrast, a minority of colocalized eQTL/GWAS variants are specific to one single tissue.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{How do trait frequencies relates to eQTL and eTissue frequency at the loci level?}

In Figure \ref{fig:region_gwas_egenes_tissues}, I have plotted the number of GWAS classes, eGenes and eTissues for regulatory variants in three pleiotropic regions.
%
All three regions are very pleiotropic with very different associated trait classes such as cancer, cardiovascular and autoimmune diseases.
%
However these plots show that the relationship between the number of traits, eGenes and eTissues can be very different.
%
The SLC22A5 locus in region 5:132,239,645-132,497,907 (5q31.1) has a low number of eGenes but a high number of eTissues.
%
By contrast, the MHC locus in region 6:31,034,839-32,478,149 (6p21.33) has a high number of both eGenes and eTissues.
%
Finally, the ATXN2 locus in region 12:111,395,984-111,645,358 (12q24.12) shows the highest trait pleiotropy but the number of eGenes and eTissues is very low.
%
In summary, trait pleiotropy can arise from different situations: few eGenes and eTissues, many eGenes and eTissues or a mix of both.

\subsection*{What are the mechanisms of pleiotropy}

Then, I wanted to understand the molecular mechanism of pleiotropic variants and regions.
%
I hypothesized that pleiotropy arises from bias in regulatory effects of variants.
%
For instance, pleiotropic variants might significantly affect some molecular functions more often.
%
Another possibility is that pleiotropic variants affect more eGenes in more eTissues, which affect more GWAS traits.

\subsection*{Which are the effect consequence of pleiotropic eQTLs?}

I first analysed whether there are significant differences of some effect consequences between more and less pleiotropic variants.
%
I separated variants according to the count of GWAS classes and computed the EBI variant effect predictor (VEP) consequence \citep{2016.Cunningham.McLaren}.
%
I found a significant larger number of missense variants among variants with 2, 3 and 4 classes compared to variants with 1 class (Fig. \ref{fig:vep_consequence}a).
%
I also found a significant larger number of splicing variants among variants with 3 classes (Fig. \ref{fig:vep_consequence}b).
%
Finally, there is also a larger of the 3'-UTR variants among variants with 4 classes (Fig. \ref{fig:vep_consequence}c).
%
% TODO Discuss sQTLs in 2021.Li.Mu.GenomeBiology.impactcelltype paper
These analyses suggest that more pleiotropic variants have a stronger effect on the coding sequence and splicing regions, which might explain partly their more pleiotropic function.

@@

Then I hypothesized that pleiotropic variants regulate more eGene even when we keep fixed the eTissue.
%
To test this hypothesis, the eGenes per variant-eTissues pairs were counted.
%
Then these eGene counts were classified according to the GWAS class count.
%
If the GWAS class count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal one.
%
I found means of eGene counts of 1.4, 1.7, 1.7 and 1.6 for GWAS classes counts 5, 4, 3 and 2 compared to eGene count mean of 1.5 for GWAS class count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic variant-eTissue pairs have slightly but significantly (Mann–Whitney U test) more eGenes compared to variants with one GWAS class (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This observation could be explained by my previous observation that pleiotropic variants have more often an effect on the splicing and 3'UTR regions (Figure \ref{fig:vep_consequence}b,c).

@@

My next hypothesis was that pleiotropic variant-eGene pairs are active in more eTissues compared with variant-eGene pairs with one GWAS class and this increases their probability to affect more GWAS classes.
%
To test this hypothesis, the eTissues per variant-eGene pairs were counted.
%
Then these eTissue counts were classified according to the GWAS class count.
%
If the GWAS class count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal GWAS class count.
%
I found means of eTissue counts of 2.2, 3, 3 and 2.6 for GWAS classes counts 5, 4, 3 and 2 compared to eTissue count mean of 2.5 for GWAS class count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).
%
This suggests that pleiotropic variant-eGene pairs are active slightly but significantly (Mann–Whitney U test) in more eTissues compared to variants with one GWAS class (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).

\subsection*{Are pleiotropic eQTLs associated to more traits in unique gene-tissue pairs?}

My next hypothesis was that pleiotropic variants are associated to more GWAS classes even after taking into account differences in eGene and eTissue counts.

To test this hypothesis, the GWAS class counts per variant-eGene-eTissue trios were counted.
%
Then these GWAS categorie counts per variant-eGene-eTissue trios were classified according to the GWAS class count per variant.
%
If the GWAS class count per variant changed in different variant-eGene-eTissue trios, then we kept the maximal GWAS class count per variant.
%
I found means of GWAS class counts per variant-eGene-eTissue of 3, 2, 1.6, 1.4 and 1 for GWAS classes counts per variant of 5, 4, 3, 2 and 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%
This shows a significant larger number of GWAS classes even in unique trios of variant-eGene-eTissue (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%
This observation could be explained by my previous observation that pleiotropic variants have more often missense effects (Fig. \ref{fig:vep_consequence}a).

@@

In Fig. \ref{fig:gwas_egene_etisue_per_variant}b, I observed that pairs of eQTL-eGene are active in more eTissues.
%
To explain this observation, I hypothesized that pleiotropic variants are active in more eTissues, because genomic regions around pleiotropic variants bind more transcription factors, which upregulate the pleiotropic regions in more tissues.
%
To test this hypothesis, I counted the number of unique transcription factors bound in a radius of 50 bp around each variant (Window of 100 bp).
%
I found a significant larger number of transcription factors bound around pleiotropic variants (Fig. \ref{fig:freq_tf_per_variant}a).

@@

\subsection*{Do pleiotropic eQTLs have stronger effect size on the gene and trait?}

Pleiotropic variants affect simultaneously more GWAS traits.
%
Therefore it is interesting to investigate how does variant causality and pleiotropy relate to effect size (beta) and significance (p-value) at the level of eQTL and GWAS traits.
%
I found that the mean of the absolute eQTL effect sizes (beta) decreased between GWAS class counts 1 and 5 (Fig. \ref{fig:beta_pval}a).
%
Regarding the eQTL significance (Negative decimal logarithm of the p-values), I found decreasing mean values for GWAS class counts between 1 and 5 (Fig. \ref{fig:beta_pval}b).

>>>>

\subsection*{How specific are eQTLs regarding traits, genes and tissues?}

Next I verified whether eQTLs tend to be specific to traits, eQTL genes and eQTL tissues.
%
74\% of eQTLs are associated to one GWAS class, 21\% are associated to 2 classes and the remaining variants associated to 3 or more trait classes make less that 4\% of eQTLs (Fig. \ref{fig:hist_gwas_egene_etissue}a).
%
Regarding eQTL genes, 36\% of the colocalized eQTL/GWAS variant modulate a single gene, 24\% modulate two genes, and the remaining 40\% modulate three or more genes (Fig. \ref{fig:hist_gwas_egene_etissue}b).
%
Concerning tissues, 27\% colocalized eQTL/GWAS variants are active in a single tissue, 16\% in two tissues, 11\% in three tissues, and the remaining 46\% in four or more tissues (Fig. \ref{fig:hist_gwas_egene_etissue}c).
%
In conclusion, trait pleiotropy is rather rare, while, regulation of least two gene in at least two tissues is rather common (Fig. \ref{fig:hist_gwas_egene_etissue}).

\subsection*{Trait, eQTL gene and tissue frequency of individual eQTLs in pleiotropic loci}

In Figure \ref{fig:region_gwas_egenes_tissues}, I have plotted the number of trait classes, eQTL genes and tissues for regulatory variants in three pleiotropic regions.
%
All three regions are very pleiotropic with very different associated trait classes such as cancer, cardiovascular and autoimmune diseases.
%
However these plots show that the relationship between pleiotropy and the number of eQTL genes and tissues is not direct.

Some regions have high number of eQTL genes and intermediate number of tissues like the interleukin locus in region 5:131912097-132802472 (5q31.1),
intermediate number of eQTL gene and variable number of tissues like the 11:65488118-65916060 locus (11q13.1),
high number of both eQTL genes and tissues like the 12:55,721,801-56,171,027 (12q13.2) region
and relatively low number of eQTL genes and tissue like the 19:48,668,049-48,756,272 locus (19q13.33) (Fig. \ref{fig:region_gwas_egenes_tissues}).

In summary, trait pleiotropy can arise in locus with variable absolute numbers of genes and tissues.

\subsection*{Where are the pleiotropic variants?}

%\subsection*{What are the mechanisms of pleiotropy}

In the following sections, I wonder about the the molecular mechanism of pleiotropic eQTLs.
%
%I hypothesized that pleiotropy arises from bias in regulatory effects of variants.
%%
%For instance, pleiotropic variants might significantly affect some molecular functions more often.
%%
%Another possibility is that pleiotropic variants affect more eGenes in more eTissues, which affect more GWAS traits.

First, I analysed whether there are significant differences of some effect consequences between more and less pleiotropic variants.
%
I separated variants according to the count of GWAS classes and computed the EBI variant effect predictor (VEP) consequence (\citep{2016.Cunningham.McLaren}).
%
I found a significant larger number of upstream, 5'-UTR, downstream and 3'-UTR variants
with 2, 3 and 4 and more classes compared to variants with one class (Fig. \ref{fig:vep_consequence}).
%
I also found a significant larger number of intron, and non-coding transcript variants
with 3 and 4 and more classes (Fig. \ref{fig:vep_consequence}).
%
These analyses suggest that more pleiotropic variants have a stronger effect on
the coding sequence and splicing regions, which might explain partly their more pleiotropic function.

@@

Then I hypothesized that pleiotropic variants modulate more genes even within the same tissues.
%
To test this hypothesis, I computed the number of eQTL genes per variant-tissue pair for different trait class counts.
%
%If the GWAS class count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal one.
%
eQTLs involved in 1, 2, 3, 4, and 5 and more GWAS classes modulate an average of 1.3, 1.5, 1.6, 1.9 and 1.8 genes, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%I found means of eGene counts of 1.4, 1.7, 1.7 and 1.6 for GWAS classes counts 5, 4, 3 and 2 compared to eGene count mean of 1.5 for GWAS class count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic eQTLs modulate more genes compared to eQTLs involved in only one GWAS class (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
More target genes of eQTLs provides an explanation to the observed pleiotropy.

@@

My next hypothesis was that pleiotropic eQTL-gene pairs are active in more tissues than non-pleiotropic eQTLs.
%
To test this hypothesis, the tissues per eQTL-gene pair was counted for eQTL involved in different GWAS class counts.
%
eQTLs involved in 1, 2, 3, 4, and 5 and more GWAS classes are active in an average of 2.4, 2.5, 2.8, 3.4 and 4.3 tissues, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic eQTL are active in more tissues (Mann–Whitney U test) compared to non-pleiotropic eQTLs (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).

%\subsection*{Are pleiotropic eQTLs associated to more traits in unique gene-tissue pairs?}
%
%My next hypothesis was that pleiotropic variants are associated to more GWAS classes even after taking into account differences in eGene and eTissue counts.
%
%To test this hypothesis, the GWAS class counts per variant-eGene-eTissue trios were counted.
%%
%Then these GWAS categorie counts per variant-eGene-eTissue trios were classified according to the GWAS class count per variant.
%%
%If the GWAS class count per variant changed in different variant-eGene-eTissue trios, then we kept the maximal GWAS class count per variant.
%%
%I found means of GWAS class counts per variant-eGene-eTissue of 3, 2, 1.6, 1.4 and 1 for GWAS classes counts per variant of 5, 4, 3, 2 and 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%%
%This shows a significant larger number of GWAS classes even in unique trios of variant-eGene-eTissue (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%%
%This observation could be explained by my previous observation that pleiotropic variants have more often missense effects (Fig. \ref{fig:vep_consequence}a).

@@

In Fig. \ref{fig:gwas_egene_etisue_per_variant}b, I observed that pairs of eQTL-gene are active in more tissues.
%
To explain this observation, I hypothesized that pleiotropic eQTLs are active in more tissues,
because genomic regions around pleiotropic variants bind more transcription factors,
which upregulate the pleiotropic regions in more tissues.
%
To test this hypothesis, I counted the number of unique transcription factors bound in a radius of 50 bp around each eQTL (Window of 100 bp).
%
eQTLs involved in 1, 2, 3 and 4 and more GWAS classes bind a mean number of 17,
19, 23 and 27 transcription factors, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%I found a significant larger number of transcription factors bound around pleiotropic variants (Fig. \ref{fig:freq_tf_per_variant}a).

@@

In summary, pleitropic eQTLs bind more unique transcription factors and are more
likely to belong to cis-regulatory modules.

\subsection*{Do pleiotropic eQTLs have stronger effect sizes?}

Pleiotropic eQTLs affect simultaneously more trait classes.
%
Therefore, I wonder about the relationship between pleiotropy, effect size and significance of eQTLs.
%
I found that the mean of the absolute eQTL effect sizes (beta) decreased between GWAS class counts 1 and 5 (Fig. \ref{fig:beta_pval}a).
%
Regarding the eQTL significance (Negative decimal logarithm of the p-values), I found decreasing mean values for GWAS class counts between 1 and 5 (Fig. \ref{fig:beta_pval}b).

### 2022-11-21 ms/ms05_floats.tex
MS

\caption{Count of GWAS classes (\textbf{a-c}), eGenes (\textbf{d-f}) and eTissues (\textbf{g-i}) in three pleiotropic genomic regions: \textbf{a,d,g}: 5:132,239,645-132,497,907 (5q31.1), \textbf{b,e,h}: 6:31,034,839-32,478,149 (6p21.33) and \textbf{c,g,i}: 12:111,395,984-111,645,358 (12q24.1). Genomic coordinates are given for the hg38 assembly.}
\label{fig:region_gwas_egenes_tissues}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 5: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
%
\caption{Odds ratio compared of the variants annotated with given variant effect predictor (VEP) consequence and given GWAS class count compared with non pleiotropic variants (GWAS class count one). The significance is given for the q-value (FDR 5\%).}
\label{fig:vep_consequence}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 6: Violin plots. eGenes, eTissues and gwas per variants
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of eGenes per variant-tissue (\textbf{a}), eTissues per variant-eGene (\textbf{b}) and GWAS classes per variant-eGene-eTissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure}

@@

\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
\end{subfigure}
%
\caption{Analysis of transcription factor binding. \textbf{a}, Binding count of transcription factors in the region surrounding pleiotropic variants (Radius 50 bp) as a function of the GWAS class count. \textbf{b}, Odds ratio of cis regulatory module-annotated vs non-annotated variants.} \label{fig:freq_tf_per_variant}
%
\end{figure}

@@

\caption{eQTL and GWAS effect size/beta (\textbf{a,b}) and eQTL and GWAS significance/p-value (\textbf{c,d}) as a function of the GWAS class count.} \label{fig:beta_pval}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 9: graphical conclusions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{\textwidth}

>>>>

\caption{Count of GWAS classes (\textbf{a-c}), eGenes (\textbf{d-f}) and eTissues (\textbf{g-i}) in three pleiotropic genomic regions: \textbf{a,d,g}: 5:132,239,645-132,497,907 (5q31.1), \textbf{b,e,h}: 6:31,034,839-32,478,149 (6p21.33) and \textbf{c,g,i}: 12:111,395,984-111,645,358 (12q24.1). Genomic coordinates are given for the hg38 assembly.}
\label{fig:region_gwas_egenes_tissues}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 5: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
%
\caption{Odds ratio compared of the variants annotated with given variant effect
predictor (VEP) consequence and given GWAS class count compared with non
pleiotropic variants (GWAS class count one). The significance is given for the
q-value (False discovery rate 5\%).}
\label{fig:vep_consequence}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 6: Violin plots. eGenes, eTissues and gwas per variants
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
%\begin{subfigure}[]{.32\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_etissue_y_gwas.py/plt.png}
%\end{subfigure}
%
\caption{Mean number of genes in eQTL-tissue pairs (\textbf{a}) and mean number of tissues in eQTL-gene pairs (\textbf{b}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure}

@@

\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
\end{subfigure}
%
\caption{Analysis of transcription factor binding.
\textbf{a}, Binding count of transcription factors in the region surrounding pleiotropic eQTLs (Radius 50 bp) as a function of the GWAS class count.
\textbf{b}, Odds ratio of eQTLs annotated with cis regulatory modules vs non-annotated.} \label{fig:freq_tf_per_variant}
%
\end{figure}

@@

\caption{eQTL and GWAS effect size/beta (\textbf{a,b}) and eQTL and GWAS significance/p-value (\textbf{c,d}) as a function of the GWAS class count.} \label{fig:beta_pval}
%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 9: graphical conclusions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{\textwidth}
